\section*{Conferences}



\begin{etaremune}
\def\labelenumi{\arabic{enumi}.}

% Belgacem, EGU 2025

\item
     Scully J. E. C., Belgacem I., Parekh R., \textbf{C. Grima}, Phillips C. B., et al. \href{https://www.hou.usra.edu/meetings/lpsc2025/pdf/1705.pdf}{Potential Landing Sites: A Comprehensive Reconnaissance Assessment of the Europa Clipper Trajectory}, 56th Lunar and Planetary Science Conference 2025, The Woodlands, TX, Abstract 1705.

\item
     \textbf{C. Grima}, W. Kofman, A. Hérique, P. Beck, S. P. S. Gulick, T. A. Goudge, \href{https://www.hou.usra.edu/meetings/lpsc2025/pdf/2393.pdf}{Frequency Dispersion of the Martian Surface Reflectivity by MARSIS}, 56th Lunar and Planetary Science Conference 2025, The Woodlands, TX, Abstract 2393.

\item
     L. Desage, K. Chan, \textbf{C. Grima}, D. A. Young, D. D. Blankenship, \href{https://www.hou.usra.edu/meetings/lpsc2025/pdf/2627.pdf}{Assessing Clutter Impacts on Reflectometry for Europa with an Antarctic Terrestrial Analogue}, 56th Lunar and Planetary Science Conference 2025, The Woodlands, TX, Abstract 2627.

\hspace{-2em}\texttt{2024 -------------}

\item
    Shadab M. A., S. Adhikari, A. Rutishauser, C. M. Stevens, \textbf{C. Grima}, M. A. Hesse, \href{https://agu.confex.com/agu/agu24/meetingapp.cgi/Paper/1526301}{Multi-scale multi dimensional infiltration in glacial firn and mechanism of ice layer and chunk formation}, AGU Fall Meeting 2024, C11C-0490, Washington DC, USA.
    
\item
    Blankenship D. D., Young D. A., Chan K., Wolfenbarger N. S., \textbf{C. Grima}, K. M. Soderlund, J. S. Greenbaum, C. Gerekos, L. Desage, J. J. Ayala, G. Steinbrügge and H. Reeves, \href{https://agu.confex.com/agu/agu24/meetingapp.cgi/Paper/1727443}{Anticipating the Subsurface of Europa’s Ice Shell: Strange? or Perhaps Familiar}, AGU Fall Meeting 2024, C22B-03, Washington DC, USA.
    
\item
    Pelle T., P. G. Myers, A. Hamilton, M. R. Mazloff, K. M. Soderlund, L. Beam, D. D Blankenship, \textbf{C. Grima}, F. Habbal, M. L. Skidmore and J. S. Greenbaum, \href{https://agu.confex.com/agu/agu24/meetingapp.cgi/Paper/1704194}{Ocean Warming, Sea Ice Decline, and Enhanced Productivity Modeled in Jones Sound, Canadian Arctic Archipelago, between 2003-2016}, AGU Fall Meeting 2024, C41E-0229, Washington DC, USA.
    
\item
    Weinstein A., J. S. Greenbaum, B. Conger and \textbf{C. Grima}, \href{https://agu.confex.com/agu/agu24/meetingapp.cgi/Paper/1573661}{Investigating the Accuracy of Orbital Stereophotogrammetry-Derived Ice-Bottom Elevation Data Sets in Antarctica}, AGU Fall Meeting 2024, ED41C-2626, Washington DC, USA.
    
\item
    Jordan M., \textbf{C. Grima}, S. P. S. Gulick, M. Prakash, C. Gerekos and G. Y. Kramer, \href{https://agu.confex.com/agu/agu24/meetingapp.cgi/Paper/1658169}{Utilizing Heterogeneities in Lunar Radar Sounder Surface Reflectivity to Identify Metallic Oxides in the Procellarum KREEP Terrane}, AGU Fall Meeting 2024, P13H-05, Washington DC, USA.
    
\item
    \textbf{Grima C.}, K. M. Soderlund, J. S Greenbaum, T. Pelle, M. R. Mazloff, D. A. Young, D. D. Blankenship, C. F. Dow, B. Schmidt, N. S. Wolfenbarger, \href{https://agu.confex.com/agu/agu24/meetingapp.cgi/Paper/1567915}{Diagnosing Ice-Water Processes with Radar Reflectometry: A Demonstration at Lake Vostok, Antarctica}, AGU Fall Meeting 2024, P23B-3218, Washington DC, USA.
    
\item
    Scully J. E. C., I. Belgacem, R. Parekh, \textbf{C. Grima}, C. B. Phillips, G. Collins, K. L. Craft, C. Detelich, E. J. Leonard, I. Mishra, G. Patterson, L. M. Prockter, S. Sutton, A. M. Stickle and D. Y. Wyrick, \href{https://agu.confex.com/agu/agu24/meetingapp.cgi/Paper/1641784}{Reconnaissance of potential landing sites by Europa Clipper}, AGU Fall Meeting 2024, P23E-3263, Washington DC, USA.
    
\item
    Prakash M., S. P. S. Gulick, \textbf{C. Grima}, C. Gerekos, M. Jordan and G. Y. Kramer, \href{https://agu.confex.com/agu/agu24/meetingapp.cgi/Paper/1611066}{Remote Sensing Investigations of Suevite in Schrödinger Basin}, AGU Fall Meeting 2024, P42B-05, Washington DC, USA.
    
\item
    Gulick S. P. S., S. Tikoo, S. Alfred, V. J. Bray, C. S. Cockell, G. S. Collins, \textbf{C. Grima}, M. A. Hesse, E. Hiatt, N. McCall, U. Nicholson, L. L. Pérez-Cruz, M. Prakash, A. Rae, J. U. Fucugauchi, \href{https://agu.confex.com/agu/agu24/meetingapp.cgi/Paper/1707094}{Role of terrestrial impact structures and scientific drilling in understanding impact processes and planetary evolution}, AGU Fall Meeting 2024, U32B-07, Washington DC, USA.

\item
    Shadab M. A., S. Adhikari, A. Rutishauser, C. M. Stevens, \textbf{C. Grima}, M. A. Hesse, \href{https://agu.confex.com/agu/agu24/meetingapp.cgi/Paper/1526301}{Multi-scale multi dimensional infiltration in glacial firn and mechanism of ice layer and chunk formation}, AGU Fall Meeting 2024, C11C-0490, Washington DC, USA.

\item
    Belgacem I., J. E. C. Scully, R. A. Parekh, C. B. Phillips, \textbf{C. Grima}, G. C. Collins, K. Craft, C. Detelich, E. Leonard, I. Mishra, G. Patterson, L. M. Prockter, S. S. Sutton, A. M. Stickle, and D. Y. Wyrick,   \href{https://submissions.mirasmart.com/DPS56/Itinerary/PresentationDetail.aspx?evdid=59}{Potential landing sites to be surveyed by Europa Clipper}, 56th Annual Meeting of the AAS Division for Planetary Sciences, 206.04, Boise, Idaho.

\item
   \textbf{Grima C.}, W. Kofman, A. Hérique, P. Beck, \href{https://drive.google.com/file/d/17kSupFJCrgi3--fEiE2FkWA5e0QUbko7/view}{Revising the Basal Permittivity of the South Polar Layered Deposits of Mars with a Surficial Dust Cover}, Texas Area Planetary Science, San Antonio, TAPS2024-01.

\item
    Belgacem I., J. E. C. Scully, R. A. Parekh, C. B. Phillips, \textbf{C. Grima}, G. C. Collins, K. Craft, C. Detelich, E. Leonard, I. Mishra, G. Patterson, L. M. Prockter, S. S. Sutton, A. M. Stickle, and D. Y. Wyrick,   \href{https://meetingorganizer.copernicus.org/EPSC2024/EPSC2024-132.html}{Potential landing sites to be surveyed by Europa Clipper}, Europlanet Science Congress, EPSC2024-132, Berlin, Germany.

\item 
    Chan K., \textbf{C. Grima}, D. D. Blankenship, \href{}{RIME-REASON synergistic opportunities for detecting near-surface layering on icy moons}, European Planetary Science Congress, Berlin, Germany, EPSC2024-691.
    
\item 
    Prakash M., Gulick S. P. S., Grima C., Jordan M. T. K., Gerekos C., \href{https://www.hou.usra.edu/meetings/metsoc2024/pdf/6311.pdf}{Investigations of a Cliff-forming Suevite Layerr in Schrodinger Basin.}, Meteoritical Society Meeting, Brussels, Belgium, \#3036.

\item 
    Belgacem I., J. Scully, R. Parekh, C. Phillips, \textbf{C. Grima}, G. Collins, K. Craft, C. Detelich, E. Leonard, I. Mishra, W. Patterson, L. Prockter, S. Sutton, A. Stickle, and D. Wyrick, \href{}{Potential landing sites to be surveyed by Europa Clipper}, European Planetary Science Congress, Berlin, Germany, \#642571

\item
    Jawin E.R., B.A. Campbell, \textbf{C. Grima}, \href{}{Seasonal CO2 Deposition at the Martian Poles as Recorded by SHARAD}, 8th International Conference on Mars Polar Science and Exploration, Abstract \#6058.

\item
     Chan K., \textbf{C. Grima}, C. Gerekos, and D. D. Blankenship, \href{https://meetingorganizer.copernicus.org/EGU24/EGU24-13404.html}{Characterizing the altitude dependence of radar reflectometry for the (near-)surface of icy worlds}, EGU General Assembly 2024, Vienna, Austria, EGU24-13404.

\item
     Gerekos C., \textbf{C. Grima}, Mastrogiuseppe M., Di Carlofelice A., Blankenship D. D., \href{https://www.hou.usra.edu/meetings/lpsc2024/pdf/1287.pdf}{Observing Solar Radio Bursts with Radar Sounders: Implications for Europa Clipper/REASON and JUICE/RIME }, 55th Lunar and Planetary Science Conference 2024, The Woodlands, TX, Abstract 1287.

\item
    \textbf{Grima C.}, W. Kofman, A. Hérique, P. Beck, Gulick S. P. S., Goudge T. A., C. Gerekos, \href{https://www.hou.usra.edu/meetings/lpsc2024/pdf/1514.pdf}{Updated Basal Detectability of an Ice Covered Mars by MARSIS}, 55th Lunar and Planetary Science Conference 2024, The Woodlands, TX, Abstract 1514.

\item
     Phillips C. B., Scully J. E. C., Cameron M. E., Craft K. L., \textbf{C. Grima}, Persaud D. M. et al., \href{https://www.hou.usra.edu/meetings/lpsc2024/pdf/1672.pdf}{A Reconnaissance Strategy for Landing on Europa, Based on Europa Clipper Data}, 55th Lunar and Planetary Science Conference 2024, The Woodlands, TX, Abstract 1672.

\item
     Gulick S. P. S., \textbf{C. Grima}, Prakash M., Gerekos C., Jordan M. T. K., Kramer G. Y., \href{https://www.hou.usra.edu/meetings/lpsc2024/pdf/2234.pdf}{Asymmetries of Schrödinger Impact Basin from Integrated Geophysics: Role of Pre-Existing Basins}, 55th Lunar and Planetary Science Conference 2024, The Woodlands, TX, Abstract 2234.

\item
     Prakash M., Gulick S. P. S., \textbf{C. Grima}, Gerekos C., Jordan M. T. K., Kramer G. Y., \href{https://www.hou.usra.edu/meetings/lpsc2024/pdf/1784.pdf}{Integrated Subsurface Radar Analyses to Characterize the Schrödinger Pyroclastic Deposit}, 55th Lunar and Planetary Science Conference 2024, The Woodlands, TX, Abstract 1784.

\item
     Jordan M. T. K., \textbf{C. Grima}, Gulick S. P. S., Prakash M., Gerekos C., Kramer G. Y., \href{https://www.hou.usra.edu/meetings/lpsc2024/pdf/1609.pdf}{Calibration of Lunar Radar Sounder Surface Reflectivity}, 55th Lunar and Planetary Science Conference 2024, The Woodlands, TX, Abstract 1609.

\item
    \textbf{[Invited Speaker] Grima C.}, \href{}{The Properties of Planetary Surfaces from Radar Sounders}, Texas Geophysical Society, University of Texas at Austin, USA

\hspace{-2em}\texttt{2023 -------------}

\item
    Scully J., C. B. Phillips, M. E. Cameron, K. L. Craft, \textbf{C. Grima}, D. Persaud, \href{https://gsa.confex.com/gsa/2023AM/meetingapp.cgi/Paper/393517}{A reconnaissance Strategy for Landing on Europa, Based on Europa Clipper Data} , The Geological Society of America GSA Connects, 201-10, Pittsburgh, USA.

\item
   Chan K., \textbf{C. Grima}, C. Gerekos, J. M. Moore, D. D. Blankenship,  \href{https://agu.confex.com/agu/fm23/meetingapp.cgi/Paper/1404410}{Near-surface Layer Characterization of Icy Moons: a Multi-bandwidth Radar Reflectometry Approach}, AGU Fall Meeting 2023, P41H-3280, San Francisco, USA.

\item
   Blankeship et al. (inc. \textbf{C. Grima}), \href{https://agu.confex.com/agu/fm23/meetingapp.cgi/Paper/1434939}{Radar for Europa Assessment and Sounding: Ocean to Near-surface (REASON)}, AGU Fall Meeting 2023, P41G-3264, San Francisco, USA.

\item
    Phillips C. B., J. E. C. Scully, M. E. Cameron, K. L. Craft, \textbf{C. Grima}, D. M. Persaud, \href{https://agu.confex.com/agu/fm23/meetingapp.cgi/Paper/1400206}{A Reconnaissance Strategy for Landing on Europa, based on Europa Clipper Data}, AGU Fall Meeting 2023, P41G-3258A, San Francisco, USA,

\item
    Daubar I. (inc. \textbf{C. Grima}), \href{https://agu.confex.com/agu/fm23/meetingapp.cgi/Paper/1425641}{Planned Geological Investigations of the Europa Clipper Mission}, AGU Fall Meeting 2023, P43B-03, San Francisco, USA,

\item
    Shadab A., S. Adhikari, A. Rutishauser, \textbf{C. Grima} and M. A Hesse,  \href{https://agu.confex.com/agu/fm23/meetingapp.cgi/Paper/1276016}{Mechanism and Factors Controlling Ice Layer Formation in Glacial Firn}, AGU Fall Meeting 2023, C43D-1632, San Francisco, USA.

\item
 Shadab A., A. Rutishauser, \textbf{C. Grima} and M. A Hesse, \href{https://agu.confex.com/agu/fm23/meetingapp.cgi/Paper/1276244}{A Unified Kinematic Wave Theory for Melt Infiltration into Firn}, AGU Fall Meeting 2023, C43D-1629A, San Francisco, USA.

\item
 \textbf{Grima C.}, K. Chan, D. D. Blankenship, and L. Bruzzone, \href{https://submissions.mirasmart.com/DPS55/Itinerary/PresentationDetail.aspx?evdid=804}{Synergistic Science at the Jovian Icy Moons with RIME and REASON}, DPS/EPSC Joint Meeting 2023, San Antonio, USA.

\item
    Gulick S. P. S., \textbf{C. Grima}, C. Gerekos, G. Kramer, and M. Jordan, \href{https://submissions.mirasmart.com/DPS55/Itinerary/PresentationDetail.aspx?evdid=992}{Integrated Measurements and Analysis of Geophysics of Schrodinger (IMAGES)}, DPS/EPSC Joint Meeting 2023, San Antonio, USA.

\item
    \textbf{[Invited Speaker] Grima C.}, \href{https://meetingorganizer.copernicus.org/EGU23/EGU23-2134.html}{Deciphering the (Near-)Surface of Planets with Nadir-pointing Radar Statistics}, EGU General Assembly 2023, Vienna, Austria, EGU23-2134.

\item
    Chan, K., \textbf{Grima C.}, D. D. Blankenship, \href{https://meetingorganizer.copernicus.org/EGU23/EGU23-10554.html}{RIME-REASON synergistic opportunities for surface and near-surface investigations of icy moons}, EGU General Assembly 2023, Vienna, Austria, EGU23-10554.

\item
    \textbf{Grima C.}, W. Kofman, A. Hérique, P. Beck, \href{https://www.hou.usra.edu/meetings/lpsc2023/pdf/1120.pdf}{Frequency Dispersion of the Martian Surface Reflectivity by MARSIS}, 54th Lunar and Planetary Science Conference 2023, The Woodlands, TX, Abstract.

\hspace{-2em}\texttt{2022 -------------}

\item
  Chan K., \textbf{C. Grima}, J. Moore and D. D. Blankenship, \href{https://meetingorganizer.copernicus.org/EPSC2022/EPSC2022-743.html?pdf}{Multi-frequency Radar Characterization of Ganymede's Near-surface}, Earth and Planetary Science Conference, Granada, Spain, \#EPSC2022-743. 
\item
  \textbf{[Invited Speaker] Grima C.}, and the REASON Team, \href{}{Assessing (Near-)Surface Properties from REASON Reflectometry}, Europa Clipper Reconnaissance Focus Group, Remote.
\item
  Gerekos C., M. Haynes, \textbf{C. Grima}, D. D. Blankenship, \href{https://www.igarss2022.org/view_paper.php?PaperNum=3558}{The Stratton-Chu Integral with a rough Facet Formulation for All-Scale Radar Sounder Simulations: Assessment with Reflectometry, IGARSS 2022, \#3558, Kuala Lumpur, Malaysia.}
\item
  Chan K., \textbf{C. Grima}, A. Rutishauser, D. A. Young, R. Culberg, D. D. Blankenship, \href{https://meetingorganizer.copernicus.org/EGU22/EGU22-6414.html}{Ice layer detection, distribution, and thickness in the near-surface firn on Devon Ice Cap: a new dual-frequency radar characterization approach}, EGU General Assembly 2022, EGU22-6414, Vienna, Austria.
\item
  Phillips. C, J. E. C. Scully, M. E. Cameron, K. L. Craft, \textbf{C. Grima}, D. M. Persaud and K. P. Hand, \href{https://agu.confex.com/data/extendedabstract/agu/abscicon21/Paper_1028516_extendedabstract_91715_0.pdf}{A Reconnaissance Strategy for Landing on Europa, based on Europa Clipper Data}, AbSciCon, Atlanta, USA, Abstract \#521-04.
\item
  Scully J. E. C., C. B. Phillips, M. E. Cameron, K. Craft, D. M. Persaud, \textbf{C. Grima}, and K. P. Hand, \href{https://agu.confex.com/data/extendedabstract/agu/abscicon21/Paper_1029989_extendedabstract_90435_0.pdf}{Applying Lessons Learned from Previous Planetary Missions to the Europa Lander Mission Concept}, AbSciCon, Atlanta, USA, Abstract \#406-03.
\item
  \textbf{[Invited Speaker] C. Grima} Hope for Present-Day Martian Groundwater Dries Up, Geology Foundation Advisory Council, March 4th Meeting, Jackson School of Geosciences, UT Austin, TX
\item
  \textbf{Grima C.}, J. Mouginot, W. Kofman, A. Hérique, P. \href{https://www.hou.usra.edu/meetings/lpsc2022/pdf/1202.pdf}{The Basal Detectability of an Ice Covered Mars by MARSIS}, 53th Lunar and Planetary Science Conference, The Woodlands, TX, Abstract \#1202.
\item
  \textbf{Grima C.}, N. E. Putzig, B. A. Campbell, M. R. Perry, S. P. Gullick, R. C. Miller, A. T. Russell, K. M. Scanlan, G. Steinbrügge, D. A. Young, S. D. Kempf, G. Ng, D. Buhl, D. D. Blankenship, \href{https://www.hou.usra.edu/meetings/lpsc2022/pdf/1198.pdf}{Martian Roughness at 15-m Scale from Radar Statistics}, 53th Lunar and Planetary Science Conference, The Woodlands, TX, Abstract \#1198.
\item
  Miller, R., \textbf{C. Grima}, S. P. S. Gulick, T. Goudge, N.E. Putzig, M.R. Perry, A. T. Russell, B.A. Campbell,  \href{https://www.hou.usra.edu/meetings/lpsc2022/pdf/1554.pdf}{Volcanic Facies and 15m Scale Roughness Throughout Athabasca Valles Lava System: A Multi-Stage Flow Development}, 53th Lunar and Planetary Science Conference, The Woodlands, TX, Abstract \#1554.
\item
  Phillips C., Scully J. E. C., Cameron M. E., Craft K. L., \textbf{Grima C.}, D. M. Persaud, and K. P. Hand, \href{https://www.hou.usra.edu/meetings/lpsc2022/pdf/2150.pdf}{A Reconnaissance Strategy for Landing on Europa, Based on Europa Clipper Data}, 53th Lunar and Planetary Science Conference, The Woodlands, TX, Abstract \#2150.
\item
  Russell, A., M. R. Perry, N. E. Putzig, \textbf{C. Grima}, R. C. Miller, S. S. Gulick, \href{https://www.hou.usra.edu/meetings/lpsc2022/pdf/2782.pdf}{Understanding Elysium Planitia Through Statistical and Standard Radar Analysis}, 53th Lunar and Planetary Science Conference, The Woodlands, TX, Abstract \#2782.
\item
  Gulick S. P. S., \textbf{Grima C.}, Gerekos C., Kramer G., \href{http://www.hou.usra.edu/meetings/lpsc2022/pdf/1739.pdf}{Geophysical Characterization Opportunities in Schrödinger Impact Basin Using Kaguya Lunar Radar Sounder and Lunar Reconaissance Orbiter}, 53th Lunar and Planetary Science Conference, The Woodlands, TX, Abstract \#1739.
\item
  Scully J., C. B. Phillips, M. E. Cameron, K. Craft, D. M. Persaud, \textbf{C. Grima}, and K. P. Hand, \href{https://www.hou.usra.edu/meetings/lpsc2022/pdf/2291.pdf}{The Application of Lessons Learned from Previous Landing and/or Sampling Missions to the Europa Lander Mission Concept}, 53th Lunar and Planetary Science Conference, The Woodlands, TX, Abstract \#2291.
\item
  \textbf{[Invited Panelist] C. Grima}, \href{https://www.europa-insitu.caltech.edu/presentations.html}{Europa Lander Speaker Series}, Caltech/JPL, online.

\hspace{-2em}\texttt{2021 -------------}

\item
   M. A. Shadab, \textbf{C. Grima}, A. Rutishauser and M. A. Hesse, \href{https://agu.confex.com/agu/fm21/meetingapp.cgi/Paper/832820}{Analytical Solutions for Melt Percolation in Ice Masses and a Pathway to Ice Lens Formation}, AGU Fall Meeting, 2021, New Orleans, LO.
\item
   \textbf{{[}Invited{]} C. Grima}, \href{https://www.hou.usra.edu/meetings/modernbrines2021/pdf/modernbrines2021_program.htm}{The Europa Clipper Mission and the Search for Brine}, Brines Across the Solar System: Modern Brines, LPI conference, October 2021, Online.
\item
   \textbf{{[}Invited{]} C. Grima}, \href{https://twitter.com/UTGeophysics/status/1377991205414375424}{Deciphering the surface and near-surface of planets with radar statistics}, UTIG seminar, Online.
\item
  \textbf{C. Grima}, N. E. Putzig, B. A. Campbell, M. R. Perry, K. M. Scanlan, \href{https://www.hou.usra.edu/meetings/lpsc2021/pdf/1221.pdf}{The Coherent Character of the Martian Surface at 20 MHz}, 52th Lunar and Planetary Science Conference, Online, Abstract 1221.
\item
  M. Liu-Schiaffini, S. Christian, R. C. Miller, \textbf{C. Grima}, G. Ng, S. S. Gullick, \href{https://www.hou.usra.edu/meetings/lpsc2021/pdf/1224.pdf}{Machine Learning Classification of the Martian Surface: Application to Radar Reflectometry}, 52th Lunar and Planetary Science Conference, Online, Abstract 1224.
\item
  \textbf{{[}Invited{]} C. Grima}, \href{https://}{Deciphering the Surface of Planetary Cryospheres with Radar Sounders}, Sci-to-Sci event, the Consulate General of France in Houston, Online.

\hspace{-2em}\texttt{2020 -------------}

\item
  K. M. Scanlan, G. Steinbruegge, \textbf{C. Grima}, D. A. Young and D. D. Blankenship, \href{https://agu.confex.com/agu/fm20/webprogram/Paper742180.html}{Impact of 1-Bit Sampling of Radar Sounding Data for Deep Space Applications: Demonstration at Mars and Implications for Europa}, AGU Fall Meeting 2020, Online.
\item
  G. Steinbrügge, D. M. Schroeder, M. Haynes, K. M. Scanlan, D. A. Young, \textbf{C. Grima}, A. Stark, H. Hussmann and D. D. Blankenship, \href{https://agu.confex.com/agu/fm20/webprogram/Paper672813.html}{Altimetry from Planetary Radar Sounders}, AGU Fall Meeting 2020, Online.
\item
  \textbf{{[}Invited{]} C. Grima}, \href{https://noc.ac.uk/seminars/liverpool/habitability-europe-its-investigation-radar-sounding}{The Habitability of Europe and its Investigation by Radar Sounding}, National Oceanography Center Seminar, Liverpool, UK, Online.
\item
  \textbf{C. Grima}, C. Gerekos,  K. M. Scanlan,  G. Steinbrugge, D. A. Young, S. D. Kempf, and D. D. Blankenship \href{https://www.hou.usra.edu/meetings/lpsc2020/pdf/1471.pdf}{Mars as an Analog to Anticipate Radar Surface Reflectivity at Europa}, 51th Lunar and Planetary Science Conference, The Woodlands, TX, Abstract 1471. \emph{[Canceled due to COVID-19]}
\item
  D. A. Young, D. D. Blankenship, N. S. Wolfenbarger, \textbf{C. Grima}, K. M. Soderlund, K. F. Chan, T. G. Richter, and the REASON Science Team, \href{https://www.hou.usra.edu/meetings/lpsc2020/pdf/2918.pdf}{An Ensemble of Point Models Approach for Science Verification and Validation for Europa Clipper's REASON (Radar for Europa Assessment and Sounding: Ocean to Near-surface}, 51th Lunar and Planetary Science Conference, The Woodlands, TX, Abstract 2918. \emph{[Canceled due to COVID-19]}
\item
  K. M. Scanlan, D. A. Young, G. Steinbrügge, \textbf{C. Grima},  S.  D.  Kempf and  D. D. Blankenship \href{https://www.hou.usra.edu/meetings/lpsc2020/pdf/1591.pdf}{Quantitative Approaches to Assess the Quality in Synthetic Aperture Radar Focusing for Orbital Radar Sounding Datasets}, 51th Lunar and Planetary Science Conference, The Woodlands, TX, Abstract 1591. \emph{[Canceled due to COVID-19]}
\item
  \textbf{{[}Invited{]} C. Grima}, \href{https://}{The Advent of Cryospheres \& the Concatenation of Worlds}, Inaugural talk to the Center for Planetary Systems and Habitability (CPSH) seminar series, UT Austin, TX.

\hspace{-2em}\texttt{2019 -------------}

\item
  D. Young, J. Greenbaum, D. Blankenship, M. Siegert, J. Roberts, T. van Ommen, A. Aitken6, \textbf{C. Grima}, E. Le Meur and The ICECAP collaboration, \href{https://agu.confex.com/agu/fm19/meetingapp.cgi/Paper/610960}{ICECAP's contribution to NASA's Operation IceBridge in East Antarctica}, AGU Fall Meeting 2019, San Francisco, CA.
\item
  S. Christian, M. Liu-Schiaffini, A. Rutishauser, K. Chan, \textbf{C. Grima} and D. Blankenship, \href{https://agu.confex.com/agu/fm19/meetingapp.cgi/Paper/588389}{Investigating Ice Surface Elevations Derived from Laser and Radar-sounding Measurements Over Devon Ice Cap, Canadian Arctic}, AGU Fall Meeting 2019, San Francisco, CA.
\item
  G. Steinbrügge, M. Haynes, K. Scanlan, D. Young, \textbf{C. Grima}, S. Kempf, D. Schroeder and D. Blankenship, \href{https://agu.confex.com/agu/fm19/meetingapp.cgi/Paper/608483}{SHARAD Altimetry on Mars: Towards an improved, global digital terrain model}, AGU Fall Meeting 2019, San Francisco, CA.
\item
  K. Scanlan, L. Beem, \textbf{C. Grima}, D. Buhl, D. Young and D. Blankenship, \href{https://agu.confex.com/agu/fm19/meetingapp.cgi/Paper/600584}{Differentiating Subglacial Drainage Patterns through the Depolarization of Airborne Radar Sounding Measurements}, AGU Fall Meeting 2019, San Francisco, CA.
\item
  K. Chan, A. Rutishauser, \textbf{C. Grima} and D. Blankenship, \href{https://agu.confex.com/agu/fm19/meetingapp.cgi/Paper/591308}{Detection of Near-Surface Frozen Brines at Europa: Radar Investigation of a Canadian Arctic Analog}, AGU Fall Meeting 2019, San Francisco, CA.
\item
  C. Gerekos, \textbf{C. Grima}, G. Steinbrügge, K. Scanlan, D. Young,
  L. Bruzzone, and D. Blankenship
  \href{https://meetingorganizer.copernicus.org/EPSC-DPS2019/EPSC-DPS2019-330.pdf}{Comparing
  the multifractal properties of Europan and Martian surfaces} EPSC-DPS
  Joint Meeting 2019, Geneva, Switzerland, Abstract EPSC-DPS2019-330.
\item
  G. Steinbrügge, J.R.C. Voigt, D.M. Schroeder, A. Stark, M.S. Haynes,
  K.M. Scanlan, C.W. Hamilton, D.A. Young, H. Hussmann, \textbf{C.
  Grima}, D.D. Blankenship
  \href{https://meetingorganizer.copernicus.org/EPSC-DPS2019/EPSC-DPS2019-865-1.pdf}{Reassessing
  Europa's Surface Roughness} EPSC-DPS Joint Meeting 2019, Geneva,
  Switzerland, Abstract EPSC-DPS2019-865.
\item
  \textbf{{[}Invited{]} C. Grima}
  \href{https://www.igsoc.org/symposia/2019/stanford/proceedings/procsfiles/procabstracts_75.html\#A3081}{Planetary
  Analogy and Radioglaciology}, Five Decades of Radioglaciology, IGS
  Symposium, Stanford, California, Abstract 81A3081.
\item
  A. Romero-Wolf, D. M. Schroeder, S. Peters, B. Bills, D. D.
  Blankenship, L. Bruzzone, B. Campbell, L. Carrer, \textbf{C. Grima},
  E. Heggy
  \href{https://www.igsoc.org/symposia/2019/stanford/proceedings/procsfiles/procabstracts_75.html\#A3009}{Status
  and prospects of passive sounding with radio-astronomical sources},
  Five Decades of Radioglaciology, IGS Symposium, Stanford, California,
  Abstract 81A3009.
\item
  K. M. Scanlan, G. Steinbruegge, S. D. Kempf, \textbf{C. Grima}, D. A.
  Young, D. D.
  Blankenship\href{https://www.igsoc.org/symposia/2019/stanford/proceedings/procsfiles/procabstracts_75.html\#A3054}{Alternative
  strategies for synthetic aperture radar focusing of orbital radar
  sounding measurements}, Five Decades of Radioglaciology, IGS
  Symposium, Stanford, California, Abstract 81A3054.
\item
  A. Rutishauser, D. D. Blankenship, L. Beem, J. S. Greenbaum, D. A.
  Young, \textbf{C. Grima}, L. N. Schwartz, J. A. Foran, A. Criscitiello
  \href{https://www.igsoc.org/symposia/2019/stanford/proceedings/programmepure.html\#Prog3055}{New
  radar-sounding investigations over the hypersaline subglacial lakes
  beneath Devon Ice Cap, Canadian Arctic}, Five Decades of
  Radioglaciology, IGS Symposium, Stanford, California, Abstract
  81A3055.
\item
  D. A. Young, \textbf{C. Grima}, G. Steinbrügge, K. M. Scanlan, S. D.
  Kempf, D. D. Blankenship
  \href{https://www.igsoc.org/symposia/2019/stanford/proceedings/programmepure.html\#Prog3056}{REASON
  for Europa: data products and algorithms}, Five Decades of
  Radioglaciology, IGS Symposium, Stanford, California, Abstract
  81A3056.
\item
  J. S. Greenbaum, D. M. Schroeder, \textbf{C. Grima}, N. Gourmelen, C.
  Dow, F. Habbal, J. Roberts, R. Warner, D. Gwyther
  \href{https://www.igsoc.org/symposia/2019/stanford/proceedings/programmepure.html\#Prog3067}{Surface
  and basal melting of the Totten Glacier Ice Shelf, East Antarctica},
  Five Decades of Radioglaciology, IGS Symposium, Stanford, California,
  Abstract 81A3067.
\item
  T. Creyts, D. M. Schroeder, \textbf{C. Grima}, W. Chu, T. M. Jordan,
  J. Paden, R. Culberg
  \href{https://www.igsoc.org/symposia/2019/stanford/proceedings/programmepure.html\#Prog3175}{Bed
  roughness as a control on the drainage of subglacial water}, Five
  Decades of Radioglaciology, IGS Symposium, Stanford, California,
  Abstract 81A3175.
\item
  \textbf{{[}Invited{]} C. Grima}
  \href{https://astronomy.utexas.edu/calendar/icalrepeat.detail/2019/05/07/1040/-/cyril-grima-ut-institute-for-geophysics?filter_reset=1\#abstract}{The
  Habitability of Europa and its Investigation by Radar Sounding},
  Department of Astronomy Colloquium, UT Austin, TX.
\item
  G. Steinbrügge, K.M.Scanlan, D.A. Young, \textbf{C. Grima},
  S.D.Kempfand and D.D. Blankenship
  \href{https://www.hou.usra.edu/meetings/lpsc2019/pdf/1993.pdf}{Sharad
  Radar Altimetry and Geodesy}, 50th Lunar and Planetary Science
  Conference (2019), The Woodlands, TX, Abstract 1993.
\item
  K. M. Scanlan, D. A. Young, \textbf{C. Grima}, G. Steinbrügge, S. D.
  Kempf and D. D. Blankenship
  \href{https://www.hou.usra.edu/meetings/lpsc2019/pdf/1994.pdf}{Englacial
  radar Attenuation Rates in the Promethei Lingula Area of the Martian
  South Polar Layered Deposits}, 50th Lunar and Planetary Science
  Conference (2019), The Woodlands, TX, Abstract 1994.
\item
  \textbf{C. Grima}, G. B. Steinbrügge, K. M. Scanlan, D. A. Young, N.
  E. Putzig, M. R. Perry, B. A. Campbell, S. D.Kempf and D. D.
  Blankenship
  \href{https://www.hou.usra.edu/meetings/lpsc2019/pdf/1280.pdf}{Deciphering
  the martian Surface and near-surface with Radar Statistiscs}, 50th
  Lunar and Planetary Science Conference (2019), The Woodlands, TX,
  Abstract 1280.

\hspace{-2em}\texttt{2018 -------------}

\item
  D. A. Young, \textbf{C. Grima}, G. Steinbrugge, K. M. Scanlan, S. D.
  Kempf, D. D. Blankenship
  \href{https://agu.confex.com/agu/fm18/meetingapp.cgi/Paper/466083}{REASON
  For Europa: Data products and algorithms}, AGU Fall Meeting 2018,
  Washington, DC, P51G-2955.
\item
  G. Steinbrugge, J. R. C. Voigt, A. Stark, B. Giese, D. M. Schroeder,
  M. Haynes, D. A. Young, \textbf{C. Grima}, H. Hussmann, D. D.
  Blankenship
  \href{https://agu.confex.com/agu/fm18/meetingapp.cgi/Paper/381734}{Reassessing
  the surface roughness of Europa using Galileo stereo images}, AGU Fall
  Meeting 2018, Washington, DC, P42B-05.
\item
  F. Habbal, J. S. Greenbaum, \textbf{C. Grima}, D. A. Young, J. L.
  Roberts, T. D. van Ommen, D. D. Blankenship
  \href{https://agu.confex.com/agu/fm18/meetingapp.cgi/Paper/454958}{
  Using radar sounding to detect grounding line positions with evidence
  of modern grounding line retreat in East Antarctica }, AGU Fall
  Meeting 2018, Washington, DC, C51F-1130.
\item
  T. T. Creyts, W. Chu, \textbf{C. Grima}, D. M. Schroeder
  \href{https://agu.confex.com/agu/fm18/meetingapp.cgi/Paper/457826}{Bed
  roughness as a control on the drainage of subglacial water}, AGU Fall
  Meeting 2018, Washington, DC, C51E-1107.\\
  -A. Rutishauser, D. D. Blankenship, L. Beem, J. S. Greenbaum, D. A.
  Young, \textbf{C. Grima}, A. S. Criscitiello
  \href{https://agu.confex.com/agu/fm18/meetingapp.cgi/Paper/465144}{
  New insights from an airborne geophysical survey over the hypersaline
  subglacial lakes beneath Devon Ice Cap, Canadian Arctic}, AGU Fall
  Meeting 2018, Washington, DC, C51E-1105.
\item
  K. Chan, \textbf{C. Grima}, D. D. Blankenship, K. M. Soderlund, D. A.
  Young
  \href{https://www.hou.usra.edu/meetings/europadeepdive2018/pdf/3015.pdf}{Dielectric
  Brine-Ice Mixtures on Europa, and the Need for New Experiments},
  Europa Deep Dive 2: Composition, \#3015, October 2018, Houston, TX.
\item
  N. S. Wolfenbarger, D. D. Blankenship, K. M. Soderlund, D. A. Young,
  and \textbf{C. Grima}
  \href{https://www.hou.usra.edu/meetings/europadeepdive2018/pdf/3036.pdf}{Leveraging
  Terrestrial Marine Ice Cores to Constrain the Composition of Ice on
  Europa}, Europa Deep Dive 2: Composition, \#3036, October 2018,
  Houston, TX.
\item
  \textbf{{[}Invited{]} C. Grima}
  \href{https://ig.utexas.edu/events/planetary-habitability/program-and-registration/week-3-habitability/}{Terrestrial
  Analogs of Icy Worlds}, Planetary Habitability Pop-Up Institute,
  Universtiy of Texas at Austin.
\item
  D. Blankenship, A. Moussessian, J. Plaut, G. W. Patterson, Y. Gim, D.
  Schroeder, K. Soderlund, D. Young, \textbf{C. Grima}, E. Chapin
  \href{}{REASON for Europa}, COSPAR Assembly (2018), Pasadena, CA,
  Paper 24665.
\item
  \textbf{C. Grima}, D. D. Blankenship, C. Paty, Y. Gim, W. Kurth, E.
  Chapin, D. M. Schroeder, J. J. Plaut, G. Patterson, A. Moussessian, D.
  A. Young \href{}{Investigating Europa's Plasma Environment from radar
  Sounding}, COSPAR Assembly (2018), Pasadena, CA, Paper 24685.
\item
  Y. Brouet, R. Cerubini, A. Pommerol, N. Thomas, L. Neves, P.
  Sabouroux. \textbf{C. Grima},
  \href{http://www.metroaerospace.org/files/MAS2018_Final.pdf}{Dielectric
  spectroscopy measurements of saline aqueous solutions in the VHF-UHF
  bands: towards a dielectric model for icy satellites water
  reservoirs}, 5th IEEE International Workshop on Metrology for
  Aerospace, Rome, Italy (2018).
\item
  B. S. Tober, J. W. Holt, \textbf{C. Grima}, J. S. Levy
  \href{https://www.hou.usra.edu/meetings/lpsc2018/pdf/2935.pdf}{Radar
  Reflectivity Analysis of Boulder Halos on Mars: Is Subsurface Ice the
  Culprit?}, 49th Lunar and Planetary Science Conference (2018),
  Houston, TX, Abstract 2935.

\hspace{-2em}\texttt{2017 -------------}

\item
  \textbf{C. Grima}, I. Koch, J.S. Greenbaum, K.M. Soderlund, D.D.
  Blankenship, D.A. Young, S. Fitzsimons.
  \href{https://agu.confex.com/agu/fm17/meetingapp.cgi/Paper/235143}{Surface
  and basal ice shelf mass balance processes of the Southern McMurdo Ice
  Shelf determined through radar statistical reconnaissance}, AGU Fall
  Meeting 2017, New Orleans, USA, C51B-0977.
\item
  J.S. Greenbaum, D.D. Blankenship, \textbf{C. Grima}, D.M. Schroeder,
  K.M. Soderlund, D.A. Young, S.D. Kempf, M.J. Siegert, J.L. Roberts,
  R.C. Warner, T.D. van Ommen.
  \href{https://agu.confex.com/agu/fm17/meetingapp.cgi/Paper/262299}{Remote
  Characterization of Ice Shelf Surface and Basal Processes: Examples
  from East Antarctica (Invited)}, AGU Fall Meeting 2017, New Orleans,
  USA, P53H-01.
\item
  A. Rutishauser, M.J. Sharp, D.D. Blankenship, M.L. Skidmore,
  \textbf{C. Grima}, D.M. Schroeder, J.S. Greenbaum, J.A. Dowdeswell,
  D.A. Young.
  \href{https://agu.confex.com/agu/fm17/meetingapp.cgi/Paper/278269}{Geophysical
  Investigations of Hypersaline Subglacial Water Systems in the Canadian
  Arctic: A Planetary Analog}, AGU Fall Meeting 2017, New Orleans, USA,
  C22A-08.
\item
  D.A. Young, \textbf{C. Grima}, J.S. Greenbaum, L. Beem, M. Cavitte, E.
  Quartini, S.D. Kempf, J.S. Roberts, M.J. Siegert, C. Ritz, D.D.
  Blankenship.
  \href{https://agu.confex.com/agu/fm17/meetingapp.cgi/Paper/292771}{The
  subglacial roughness of Antarctica: Analogs, interpretation and
  implications for ice thickness uncertainities}, AGU Fall Meeting 2017,
  New Orleans, USA, C32A-05.
\item
  K. Chan, \textbf{C. Grima}, D. D. Blankenship, D. A. Young, K. M.
  Soderlund.
  \href{http://www.hou.usra.edu/meetings/europadeepdive2017/pdf/sess201.pdf}{Mobilization
  of Near-Surface Brine on Europa}. Europa Deep Dive 1: Ice Shell
  Exchange Processes, Houston, Tx, \#7014.
\item
  F. Habbal, J. S. Greenbaum, \textbf{C. Grima}, D. A. Young, J.
  Roberts, T. van Ommen, and D. D. Blankenship.
  \href{http://meetingorganizer.copernicus.org/EGU2017/EGU2017-1526.pdf}{Improved
  grounding line constraints and evidence of retreat of Totten Glacier,
  East Antarctica}, EGU General Assembly, Vienna, Austria,
  \#EGU2017-1526.
\item
  J. S. Greenbaum, D. M. Schroeder, \textbf{C. Grima}, F. Habbal, C.
  Dow, J. Roberts, D. Gwyther, T. van Ommen, M. Siegert, and D. D.
  Blankenship,
  \href{http://meetingorganizer.copernicus.org/EGU2017/EGU2017-1559.pdf}{Morphological
  evidence and direct estimates of rapid melting beneath Totten Glacier
  Ice Shelf, East Antarctica}, EGU General Assembly, Vienna, Austria,
  \#EGU2017-1559.
\item
  Steinbrügge G., D. M. Schroeder, M. S. Haynes, H. Hussmann, \textbf{C.
  Grima}, and D. D. Blankenship,
  \href{http://meetingorganizer.copernicus.org/EGU2017/EGU2017-9205.pdf}{Assessing
  the potential for measuring Europa's tidal Love number h2 using radar
  sounder and topographic imager data}, EGU General Assembly, Vienna,
  Austria, \#EGU2017-9205.
\item
  \textbf{Grima C.}, Blankenship D.D., Paty C., Gim Y., Kurth W. S., et
  al.
  \href{http://www.lpi.usra.edu/meetings/lpsc2017/pdf/2816.pdf}{Investigating
  Europa's Plasma Environment from Radar Sounding}, LPSC XLVIII, The
  Woodlands, Texas, \#2816.
\item
  Blankenship D.D., \textbf{Grima C.}, Young D.A., SchroederD.M.,
  Soderlund K.M., et al.
  \href{http://www.lpi.usra.edu/meetings/lpsc2017/pdf/2888.pdf}{Understanding
  Europa's Ice Shell and Subsurface Water Through Terrestrial Aanalogs
  for Flyby Radar Sounding}, LPSC XLVIII, The Woodlands, Texas, \#2888.

\hspace{-2em}\texttt{2016 -------------}

\item
  \textbf{Grima C.}, E. Lopez Garcia, I. Koch, J.S. Greenbaum, K.M.
  Soderlund, D.D. Blankenship, D.A. Young, S. Fitzsimons,
  \href{https://agu.confex.com/agu/fm16/meetingapp.cgi/Paper/197146}{
  Surface Density, Roughness, and Brine Infiltration Observed with
  Airborne Radar Statistical Reconnaissance at The McMurdo Ice Shelf,
  Antarctica }, AGU 2016, San Francisco, C53A-0701.
\item
  Rutishauser A., \textbf{C. Grima}, M.J. Sharp, Blankenship D.D., D.A.
  Young D.A. F. Cawkwell, J.A. Dowdeswell,
  \href{https://agu.confex.com/agu/fm16/meetingapp.cgi/Paper/152238}{Characterizing
  near-surface firn from the scattered signal component of glacier
  surface reflections detected in airborne radio-echo sounding
  measurements}, AGU 2016, San Francisco, C13C-0839.
\item
  Schroeder D. M., \textbf{C.Grima}, M. Haynes, J. Greenbaum,
  \href{http://www.igsoc.org/symposia/2016/lajolla/proceedings/procsfiles/procabstracts_69.html\#A1991}{Distinguishing
  the signatures of ice shelf surface roughness, basal roughness,
  temperature and chemistry in radar sounding data}. International
  Symposium on Interactions of Ice Sheets and Glaciers with the Ocean.
  La Jolla, California, USA, Abs \#74A1991.
\item
  Poggiali V., M. Mastrogiuseppe, A. Hayes, R. Seu, S. Birch, R. Lorenz,
  \textbf{C. Grima}, J. Kargel, and J. Hofgartner,
  \href{http://meetingorganizer.copernicus.org/EGU2016/EGU2016-8065.pdf}{Liquid-filled
  Canyons on Titan}, European Geosciences Union General Assembly,
  EGU2016-8065.
\item
  Bergeot N., Witasse O., Kofman W., \textbf{C. Grima}, Mouginot J.,
  Peter K., Pätzold M., and V. Dehant,
  \href{http://meetingorganizer.copernicus.org/EGU2016/EGU2016-3196.pdf}{Study
  of the Total Electron Content in Mars ionosphere from MARSIS data
  set}, European Geosciences Union General Assembly, EGU2016-3196.
\item
  \textbf{Grima C.}, M. Mastrogiuseppe, A. Hayes, S. Wall, B. Stiles, C.
  Elachi,
  \href{http://www.hou.usra.edu/meetings/lpsc2016/pdf/1660.pdf}{Radar
  Statistical Reconnaissance with the Cassini RADAR: Roughness of
  Titan's Seas}, LPSC, The Woodlands, Texas, \#1660.
\item
  N. E. Putzig, G. A. Morgan, B. A. Campbell, \textbf{C. Grima}, I. B.
  Smith, R. J. Phillips, and M. Golombek,
  \href{http://www.hou.usra.edu/meetings/lpsc2016/pdf/1655.pdf}{Radar
  properties of the proposed InSight landing site in Western Elysium
  Planitia on Mars}, LPSC, The Woodlands, Texas, \#1655.

\hspace{-2em}\texttt{2015 -------------}

\item
  Castelletti D., Schroeder D.M., Hensley S., \textbf{Grima C.}, Ng G.,
  D. Young, Yonggyu Gim, Bruzzone L., A. Moussessian, Blankenship D.D.,
  \href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?reload=true\&arnumber=7325950}{Clutter
  detection using two-channel radar sounder data}, Geoscience and Remote
  Sensing Symposium (IGARSS), 2015 IEEE International, 26-31 July 2015,
  Milan , p. 1052-55.
\item
  Poggiali V., Mastrogiuseppe M., Hayes A., Seu R., Birch S., Hofgartner
  J., Flamini E., Lorenz R., \textbf{Grima C.}, Kargel K., Mullen J.,
  \href{https://agu.confex.com/agu/fm15/meetingapp.cgi/Paper/83937}{Liquid-Filled
  Chanels on Titan}, AGU 2015, San francisco, P12B-02.
\item
  Moussessian A., Blankenship D., Plaut J., Gim Y., Schroeder D.,
  Soderlund K., \textbf{Grima C.}, Young D., Chapin E.,
  \href{https://agu.confex.com/agu/fm15/meetingapp.cgi/Paper/84483}{REASON
  for Europa}, AGU 2015, San francisco, P13E-05.
\item
  Schroeder D., \textbf{Grima C.}, Haynes M.,
  \href{https://agu.confex.com/agu/fm15/meetingapp.cgi/Paper/61923}{Surface
  and Basal Roughness in Radar Sounding Data: Obstacle and Opportunity},
  AGU 2015, San francisco, C13D-03.
\item
  Blankenship D., \textbf{Grima C.}, Young D., Schroeder D., Soderlund
  K., Gim Y., Plaut J., Patterson G., Moussessian A.,
  \href{https://agu.confex.com/agu/fm15/meetingapp.cgi/Paper/85704}{Understanding
  Europa's Ice Shell and Subsurface Water through Terrestrial Analogs
  for Flyby Radar Sounding}, AGU 2015, San francisco, P53G-02.
\item
  \textbf{Grima C.}, Blankenship D., Schroeder D., Moussessian A.,
  Soderlund K., Gim Y., Plaut J., Greenbaum J., Lopez Garcia E.,
  Campbell B., Putzig N., Patterson G.
  \href{https://agu.confex.com/agu/fm15/meetingapp.cgi/Paper/83156}{Surface
  Reflectometry and Ionosphere Sounding from the Radar for Europa
  Assessment and Sounding: Ocean to Near-surface (REASON)}, AGU 2015,
  San francisco, P11C-2110.
\item
  Blankenship, A. Moussessian, K.M. Soderlund, \textbf{C. Grima}, D.A.
  Young, D.M. Schroeder, Y. Gim, J.J. Plaut, G.W. Patterson,
  \href{http://www.hou.usra.edu/meetings/abscicon2015/pdf/7627.pdf}{Revealing
  secret's of Europa's ice shell, hidden water and plume activity
  through flyby radar sounding}, Astrobiology Science Confererence,
  Chicago, \#7627.
\item
  \textbf{{[}Invited{]} C. Grima} Lecture at UTIG Brownbag at UTIG,
  \href{http://www-udc.ig.utexas.edu/external/seminars/seminars/brownbag.htm}{How
  to carefully operate a radar in the space environment of Europa?}.
\item
  Rutishauser A., \textbf{Grima C}., Sharp M., Blankenship D. D., Young
  D. A., Dowdeswell J. A., The use of airborne radar reflectometry to
  derive near-surface snow/firn properties on Devon Ice Cap, Canadian
  Arctic. IASC Network Arctic Glaciology Annual Meeting, University
  Centre Obergurl, Austria.
\item
  \textbf{Grima C.} and Blankenship. D. D.
  \href{http://www.hou.usra.edu/meetings/lpsc2015/pdf/1238.pdf}{Radar
  Statistical reconnaissance of the 2016 Insight landing sites}. LPSC,
  The Woodlands, Texas, \#1238.
\item
  Lalich D. Holt J. W. \textbf{Grima C.}
  \href{http://www.hou.usra.edu/meetings/lpsc2015/pdf/2430.pdf}{Heterogeneity
  of SHARAD Reflectivity in the NPLD: Implications for the Climate
  Record}. LPSC, The Woodlands, Texas, \#2430.

\hspace{-2em}\texttt{2014 -------------}

\item
  \textbf{Grima C.}, Rosales, BlankenshipD. D., Young D. A..
  \href{https://agu.confex.com/agu/fm14/meetingapp.cgi/Paper/22986}{McMurdo
  Ice Shelf Sounding and Radar Statistical Reconnaissance at 60-MHz:
  Brine Infiltration Extent and Surface Properties}. AGU Fall meeting,
  San Francisco, \#C21C-0372.
\item
  Rutishauser A., \textbf{Grima C.}, Sharp, Blankenship, Young,
  Dowedeswell.
  \href{https://agu.confex.com/agu/fm14/meetingapp.cgi/Paper/17159}{The
  use of airborne radar reflectometry to establish snow/firn density
  distribution on Devon Ice Cap, Canadian Arctic: A path to
  understanding complex heterogeneous internal layering patterns}. AGU
  Fall meeting, San Francisco, \#C21C-0352.
\item
  Palmer, Dowdeswell, Christoffersen, Benham, Young, Blankenship,
  Richter, Ng, \textbf{Grima C.}, Habbal, Sharp.
  \href{https://agu.confex.com/agu/fm14/meetingapp.cgi/Paper/15672}{Airborne
  geophysical survey of ice caps in the Queen Elizabeth Islands, Arctic
  Canada}. AGU Fall meeting, San Francisco, \#C21C-0360.
\item
  Schroeder D.M., \textbf{Grima C.}, Blankenship D.D.
  \href{https://agu.confex.com/agu/fm14/meetingapp.cgi/Paper/8154}{Characterizing
  Englacial Attenuation and Grounding Zone Geometry Using Airborne Radar
  Sounding}. AGU Fall meeting, San Francisco, \#C53B-0303.
\item
  \textbf{{[}Invited{]} C. Grima} UTIG Seminar
  \href{http://mediasite.jsg.utexas.edu/UTMediasite/Play/7b4636e8db6844d79de9e32a14f142781d}{Leveraging
  Radar Sounding with Surface Reconnaissance: From Antarctic Science to
  Planetary Landing Sites}, UTIG, Austin, TX.
\item
  Schroeder D. M., Burch C. B., Soderlund K. M., \textbf{Grima C.},
  Blankenship D. D., Komacek T. D., Quinn T. M., Van Hecke M. A.,
  Schmidt B. E., Patterson G. W., Plaut J. J. \href{https://www.lpi.usra.edu/lpi/contribution_docs/LPI-001774.pdf}{Icy world science and
  habitability in the national science olympiad for middle school
  students}. Workshop on the habitability of Icy Worlds, Pasadena,
  California, USA.
\item
  \textbf{Grima C.}, Schroeder D. M., Blankenship D. D., Young D A.
  \href{https://www.lpi.usra.edu/lpi/contribution_docs/LPI-001774.pdf}{Europa landing site selection supported by ice penetrating radar}.
  Workshop on the habitability of Icy Worlds, Pasadena, California, USA.
\item
  Blankenship D. D., Moussessian A., Schroeder D. M., Soderlund K.,
  \textbf{Grima C.}, Gim Y., Plaut J. J., Schmidt B. E. \href{https://www.lpi.usra.edu/lpi/contribution_docs/LPI-001774.pdf}{Flyby sounding
  of europa's icy shell: radar investigations,
  analogs, and instruments for the europa clipper mission}. Workshop on
  the habitability of Icy Worlds, Pasadena, California, USA.

\hspace{-2em}\texttt{2013 -------------}

\item
  \textbf{Grima C.}, Schroeder D. M., Blankenship D. D., Young D. A..
  Planetary surface roughness derived from ice penetrating radar data:
  Method and concept validation in Antarctica. AGU Fall Meeting, San
  Francisco, California, USA. (2013) Grima C., Schroeder D. M.,
  Blankenship D. D., Young D. A.. Firn variability derived from a
  statistical analysis of airborne ice penetrating radar over the
  Thwaites Glacier catchment, West Antarctica. IGS Int. Glacio. Soc.
  Symp. on Radioglaciology, Lawrence, Kansas, USA.
\item
  \textbf{Grima C.}, Schroeder D. M., Blankenship D. D., Young D. A.
  Identifying Surface Characteristics with an Ice Penetrating Radar
  Sounder at Europa: Potential for Landing Site selection. Lun. and
  Planet. Sc. Congress, The Woodlands, Texas, USA.
\item
  Blankenship D. D., Schroeder D. M., Soderlund K. M., \textbf{Grima C.}
  Flyby sounding ofEurope\textbackslash{}u2019s icy shell: radar
  investigations, analogs, and instruments for the Europe Clipper
  Mission. IGS Int. Glacio. Soc. Symp. on Radioglaciology, Lawrence,
  Kansas, USA.
\item
  Arnold E., Curra C., Karowski B., Schroeder D. M., \textbf{Grima C.},
  Young D. A., Blankenship D. D. How to enhance Europa surface
  characterization with an ice penetrating radar? Comparative study in
  Antarctica. AGU Fall meeting, San Francisco.

\hspace{-2em}\texttt{2012 -------------}

\item
  Palmer S. J., Dowdeswell J. A., Christoffersen P., Young D. A.,
  Blankenship D. D., Stiegert M. J., Bamber, J. L., Greenbaum J. S., Ng
  G., \textbf{Grima C.} Airborne geophysical investigation of basal
  conditions at flow transitions of 16 Greenland Ice Sheet outlet
  glaciers. AGU meeting, San Francisco, USA.
\item
  \textbf{{[}Invited{]} Grima C.} Lecture at IPAG, \emph{"Exploiter la
  nature statistique de l'écho radar pour la caractérisation des
  surfaces planétaires"}, France.
\item
  \textbf{{[}Invited{]} Grima C.} Lecture at LEGOS, \emph{"Exploiter la
  nature statistique de l'écho radar pour la caractérisation des
  surfaces planétaires"}, France.

\hspace{-2em}\texttt{2011 -------------}

\item
  Kofman W., \textbf{Grima C.}, Hérique A., Seu R., Radar reflectivity
  of the surface of Mars at 20 MHz from SHARAD: Cartography and
  quantitative analysis. AGU meeting, San Francisco, USA.

\hspace{-2em}\texttt{2010 -------------}

\item
  \textbf{Grima C.}, Kofman W. Hérique A., Seu R., Physical parameters
  of the near-surface of mars derived from sharad radar reflectivity:
  statistical approach. 38th COSPAR scientific assembly, Bremen,
  Germany.

\hspace{-2em}\texttt{2009 -------------}

\item
  Pommerol A., Mouginot J., Kofman W., Safaeinili A., Plaut J.J.,
  \textbf{Grima C.}, Herique A., and Beck P. Martian surface radar
  reflectivity from MARSIS soundings, AGU meeting, San Francisco, USA.
\item
  Pommerol A., Kofman W., Audouard J., Kobayashi T., \textbf{Grima C.},
  Mouginot J., Beck P., and Ono T., Characterization and mapping of the
  Lunar subsurface by the LRS/SELENE radar sounder : methods and
  preliminary results, Europ. Planet. Sci. Congress, Potsdam, Germany.
\item
  Kofman W., Mouginot J., Beck P., Pommerol A., Schmitt B.,
  \textbf{Grima C.}, Herique A., Safaeinili A., and Plaut J.J., Mars
  surface materials from MARSIS radar reflectivity, AGU meeting, San
  Francisco, USA.
\item
  \textbf{Grima C.}, Kofman W., Hérique A., Beck P., and Seu R., Mapping
  the radar reflectivity of the Martian surface with the SHAllow RADar
  (SHARAD), Europ. Planet. Sci. Congress, Potsdam, Germany.
\item
  \textbf{Grima C.}, Costard F., Kofman W., Clifford S.M., Mouginot J.,
  Servain A., Herique A., and Seu R., Studying the geomorphology of
  unusual glacial scarps on Mars, using a multi-instrumental approach,
  Journées de la SF2A, Besançon, France.
\item
  \textbf{Grima C.}, Costard F., Kofman W., Clifford S.M., Mouginot J.,
  Servain A., Herique A., and Seu R. Large and assymetric polar scarps
  in Planum, Mars : Characterization and evolution. AGU meeting, San
  Francisco, USA.

\hspace{-2em}\texttt{2008 -------------}

\item
  Mouginot J., Kofman W., Safaeinili A., \textbf{Grima C.}, Hérique A.,
  Plaut J., and Picardi G. Thickness of south residual cap of Mars by
  MARSIS. COSPAR scientific assembly, Montreal, Canada.
\item
  Mouginot J., Kofman W., \textbf{Grima C.}, Safaeinili A., and Plaut J.
  Martian Surface Reflectivity seen by MARSIS. AGU meeting, San
  Francisco, USA.
\item
  Kofman W., \textbf{Grima C.}, Mouginot J., Hérique A., Seu R., Bicarri
  D., and Orosei R. 3D modeling of south polar layered deposits on Mars
  with SHARAD radar data. Europ. Planet. Sci. Congress, Potsdam,
  Germany.
\item
  \textbf{Grima C.}, Kofman W., Mouginot J., Servain A., Beck P.,
  Pommerol A., Hérique A., and Seu R. Unusual ice scarps on Mars : an
  origin highlighted by radar sounding, elevation data, and visible
  imagery. Int. Symp. on Radioglacio. and its App., Madrid, Spain.
\item
  \textbf{Grima C.}, Kofman W., Mouginot J., Servain A., Beck P.,
  Pommerol A., Hérique A., and Seu R. Surface and subsurface study of
  unusual ice scarps, southern polar cap of Mars. 37th COSPAR scientific
  assembly, Montreal, Canada.

\hspace{-2em}\texttt{2007 -------------}

\item
  Kofman W., \textbf{Grima C.}, Mouginot J., Herique A., Seu R., Biccari
  D., Orosei R. 3D Modeling of South Poar Layered Deposits on Mars with
  SHARAD radar data. EuroPlanet Science Congress, Berlin, Germany,
  Vol.2., EPSC2007-A-00554, 2007.

\hspace{-2em}\texttt{2006 -------------}

\item
  Gunell H., H. Nilsson, U. V. Amerstorfer, E. Carlsson, \textbf{C. Grima}, and
  the Aspera-3 Team. Plasma instabilities near Mars. 36th COSPAR
  Scientific Assembly, Beijing, China. \#2338
  
\end{etaremune}