\section*{Refereed Publications (\href{https://scholar.google.com/citations?user=kaUVku0AAAAJ&hl=fr}{\aiGoogleScholar $\,$ Metrics})}

($\clubsuit$ Mentored Student, $\spadesuit$ Postdoc Collaborator, Former Advisor$^\lozenge$, \aiOpenAccessSquare $\,$ Open Access)
\vspace{1em}

% In Review
\textbf{In Review}
\begin{itemize}

\item
  R. Lorenz, E. Leonard, K. Miller, M. Hedman, L. C. Quick, T. M. Becker, S. Brooks2, C. Cochrane, A. G Davies, C. M. Ernst, \textbf{C. Grima}, C. J. Hansen, C. Howett, S. Hsu11, X. Jia, A. Luspay-Kuti, M. Kivelson, F. Klenner, A. McEwen, W. B. McKinnon, F. Postberg, J. Rathbun, K. D. Retherford, K. Scanlan, K. M. Seaton, J. Spencer, J. H. Waite, P. Withers, D. Wyrick, M. Y. Zolotov24, and the Europa Clipper Plume Focus Group, \href{}{Plume Activity on Europa: Current Knowledge and Search Strategy for Europa Clipper}, \texttt{(submitted)}, \ul{Space Science Reviews}.

\item
  E. Jawin, B. Campbell, \textbf{C. Grima}, \texttt{(submitted)}, \href{}{Seasonal CO2 cycle at the martian poles revealed by sounding radar}, \ul{Geophysical Research Letters}.

\item
  T. Pelle, P. G. Myers, A. Hamilton, M. Mazloff, K. M. Soderlund, L. Beem, D. D. Blankenship, \textbf{C. Grima}, F. Habbal, M. Skidmore, and J. S. Greenbaum, \texttt{(submitted)}, \href{}{Ocean circulation, sea ice, and productivity simulated in Jones Sound, Canadian Arctic Archipelago, between 2003-2016}, \ul{Ocean Science }.

\item
  J. E. C. Scully, I. Belgacem, R. Parekh, \textbf{C. Grima}, C. B. Phillips, K. L. Craft, G. C. Collins, C. Detelich, E. J. Leonard, I. Mishra, G. Wesley Patterson, L. M. Prockter, An M. Stickle, S. S. Sutton, \texttt{(submitted)}, \href{}{Potential landing sites: a comprehensive reconnaissance assessment of the Europa Clipper trajectory}, \ul{The Planetary Science Journal}.

\item
  $\clubsuit$ M. A. Shadab, \textbf{C. Grima}, A. Rutishauser, M. A. Hesse, \texttt{(submitted)}, \href{}{A unified kinematic wave theory for melt infiltration into firn}, \ul{Journal of Glaciology}. 

\item
  C. B. Phillips et al., (inc. \textbf{C. Grima}), \texttt{(submitted)}, \href{}{A Reconnaissance Strategy for Landing on Europa, based on Europa Clipper Data}, \ul{The Planetary Science Journal}. 

\end{itemize}


% Published
\textbf{Published}

\begin{etaremune}

\item
  N. S. Wolfenbarger, D. D. Blankenship, D. A. Young, K. M. Scanlan, C. J. Chivers, D. Findlay, G. B. Steinbrügge, K. Chan, \textbf{C. Grima}, K. M. Soderlund, and D. M. Schroeder, \texttt{(2025)}, \href{https://agupubs.onlinelibrary.wiley.com/doi/full/10.1029/2024GL109144}{The Potential for Salt Layers in Europa’s Ice Shell as Radar-Detectable Structure} \aiOpenAccessSquare, \ul{Geophysical Research Letters}.

\item
  $\clubsuit$ M. A. Shadab, S. Adhikari, A. Rutishauser, \textbf{C. Grima}, M. A. Hesse, (2024). \href{https://doi.org/10.1029/2024GL109893}{A Mechanism for Ice Layer Formation in Glacial Firn \aiOpenAccessSquare}. Geophysical Research Letters 51, e2024GL109893.

\item
  D.D. Blankenship, A. Moussessian, E. Chapin, D.A. Young, G. Wesley Patterson, J.J. Plaut, A.P. Freedman, D.M. Schroeder, \textbf{C. Grima}, G. Steinbrügge, K.M. Soderlund, T. Ray, T,G, Richter, L. Jones-Wilson, N.S. Wolfenbarger, K.M. Scanlan, C. Gerekos, K. Chan, I. Seker, M.S. Haynes, A.C. Barr Mlinar, L. Bruzzone, B.A. Campbell, L.M. Carter, C. Elachi, Y. Gim, A. Hérique, H. Hussmann, W. Kofman, W.S. Kurth, M. Mastrogiuseppe, W.B. McKinnon, J.M. Moore, F. Nimmo, C. Paty, D. Plettemeier, B.E. Schmidt, M.Y. Zolotov, P.M. Schenk, S. Collins, H. Figueroa, M. Fischman, E. Tardiff, A. Berkun, M. Paller, J.P. Hoffman, A. Kurum, G.A. Sadowy, K.B. Wheeler, E. Decrossas, Y. Hussein, C. Jin, F. Boldissar, N. Chamberlain, B. Hernandez, E. Maghsoudi, J., Mihaly, J., Worel, S., Singh, V., Pak, K., Tanabe, J., Johnson, R., Ashtijou, M., Alemu, T., Burke, M., Custodero, B., Tope, M.C., Hawkins, D., Aaron, K., Delory, G.T., Turin, P.S., Kirchner, D.L., Srinivasan, K., Xie, J., Ortloff, B., Tan, I., Noh, T., Clark, D., Duong, V., Joshi, S., Lee, J., Merida, E., Akbar, R., Duan, X., Fenni, I., Sanchez-Barbetty, M., Parashare, C., Howard, D.C., Newman, J., Cruz, M.G., Barabas, N.J., Amirahmadi, A., Palmer, B., Gawande, R.S., Milroy, G., Roberti, R., Leader, F.E., West, R.D., Martin, J., Venkatesh, V., Adumitroaie, V., Rains, C., Quach, C., Turner, J.E., O’Shea, C.M., Kempf, S.D., Ng, G., Buhl, D.P., Urban, T.J., (2024). \href{https://doi.org/10.1007/s11214-024-01072-3}{Radar for Europa Assessment and Sounding: Ocean to Near-Surface (REASON)}. \ul{Space Science Reviews} 220. 


\item
  \textbf{C. Grima}, W. Kofman$^\lozenge$, A. Hérique, P. Beck, \texttt{(2024)}, \href{https://agupubs.onlinelibrary.wiley.com/doi/10.1029/2024GL109085}{Revising the Basal Permittivity of the South Polar Layered Deposits of Mars with a Surficial Dust Cover \aiOpenAccessSquare}, \ul{Geophysical Research Letters} 51(12), 9pp.
  
\item
  T. M Becker, A.G. Hayes, G.C. Collins, K.L. Craft, J.A. Rathbun, J.R. Spencer, D.Y. Wyrick, M.T. Bland, A.G. Davies, C.M. Ernst, S.M. Howell, E.J. Leonard, A.S. McEwen, J.M. Moore, C.B. Phillips, L.M. Prockter, L.C. Quick, J.E.C. Scully, J.M. Soderblom, S.M. Brooks, M. Cable, M.E. Cameron, K. Chan, C.J. Chivers, M. Choukroun, C.J. Cochrane, S. Diniega, A.J. Dombard, C.M. Elder, C. Gerekos, C. Glein, T.K. Greathouse, \textbf{C. Grima}, M.S. Gudipati, K.P. Hand, C. Hansen, P. Hayne, M. Hedman, K. Hughson, X. Jia, J. Lawrence, H.M. Meyer, K. Miller, R. Parekh, G.W. Patterson, D.M. Persaud, S. Piqueux, K.D. Retherford, K.M. Scanlan, P. Schenk, B. Schmidt, D. Schroeder, G. Steinbrügge, A. Stern, G. Tobie, P. Withers, D.A. Young, B. Buratti, H. Korth, D. Senske, and R. Pappalardo \texttt{(2024)}, \href{https://link.springer.com/article/10.1007/s11214-024-01069-y}{Exploring the Composition of Europa with the upcoming Europa Clipper mission \aiOpenAccessSquare}, \ul{Space Science Reviews} 220(49).

\item
  I. J. Daubar, A. G. Hayes, G. C. Collins, K. L. Craft, J. A. Rathbun, J. R. Spencer, D. Y. Wyrick, M. T. Bland, A. G. Davies, C. M. Ernst, S. M. Howell, E. J. Leonard, A. S. McEwen, J. M. Moore, C. B. Phillips, L. M. Prockter, L. C. Quick, J. E. C. Scully, J. M. Soderblom, S. M. Brooks, M. Cable, M. E. Cameron, K. Chan, C. J. Chivers, M. Choukroun, C. J. Cochrane, S. Diniega, A. J. Dombard, C. M. Elder, C. Gerekos, C. Glein, T. K. Greathouse, \textbf{Grima, C.}, M. S. Gudipati, K. P. Hand, C. Hansen, P. Hayne, M. Hedman, K. Hughson, X. Jia, J. Lawrence, H. M. Meyer, K. Miller, R. Parekh, G. W. Patterson, D. M. Persaud, S. Piqueux, K. D. Retherford, K. M. Scanlan, P. Schenk, B. Schmidt, D. Schroeder, G. Steinbrügge, A. Stern, G. Tobie, P. Withers, D. A. Young, B. Buratti, H. Korth, D. Senske, and R. Pappalardo, \texttt{(2024)}, \href{https://link.springer.com/article/10.1007/s11214-023-01036-z?utm_source=rct_congratemailt&utm_medium=email&utm_campaign=oa_20240212&utm_content=10.1007/s11214-023-01036-z}{Planned Geological Investigations of the Europa Clipper Mission \aiOpenAccessSquare}, \ul{Space Science Reviews} 220(18), 55pp.

\item
  $\clubsuit$ R. C. Miller, \textbf{C. Grima}, Gulick S. P. S., Goudge T. A., Russell A., Perry M., Putzig N., Campbell B., \texttt{(2024)}, \href{https://doi.org/10.1016/j.icarus.2023.115691}{Dynamic Development of the Athabasca Valles Outflow System from Volcanic Facies and 15-m Scale Roughness \aiOpenAccessSquare}, \ul{Icarus}: Mars Reconnaissance Orbiter Special Issue, 21pp, v419, 115691.  

\item
  $\clubsuit$ K. Chan, \textbf{C. Grima}, A. Rutishauser, D. A. Young, R. Culberg, and D. D. Blankenship$^\lozenge$, \texttt{(2023)}, \href{https://tc.copernicus.org/preprints/tc-2022-181/}{Spatial characterization of near-surface structure and meltwater runoff conditions across Devon Ice Cap from dual-frequency radar reflectivity \aiOpenAccessSquare}, \ul{The Cryosphere}, tc-2022-181, 14 p.

\item
  \textbf{C. Grima}, N. E. Putzig, B. A. Campbell, M. Perry, S. P. S. Gulick, R. C. Miller, A. T. Russell, K. M. Scanlan, G. Steinbrügge, D. A. Young, S. D. Kempf, G. Ng, D. Buhl, and D. D. Blankenship$^\lozenge$, \texttt{(2022)}, \href{https://doi.org/10.3847/PSJ/ac9277}{Investigating the Martian Surface at Decametric Scale: Population, Distribution and Dimension of Hetereogeneities from Radar Statistics \aiOpenAccessSquare}, \ul{The Planetary Science Journal} 3(10), 14pp.

\item
  $\clubsuit$ M. Liu-Schiaffini, G. Ng, \textbf{C. Grima} and D. Young, \texttt{(2022)}, \href{https://ieeexplore.ieee.org/document/9916288}{Ice Thickness from Deep Learning and Conditional Random Fields: Application to Ice Penetrating RadarData with Radiometric Validation}, \ul{IEEE Transactions on Geoscience and Remote Sensing} vol.60, 5119014, 14pp.

\item
  \textbf{C. Grima}, J. Mouginot, W. Kofman$^\lozenge$, A. Hérique and P. Beck, \texttt{(2022)}, \href{https://doi.org/10.1029/2021GL096518}{The Basal Detectability of an ice-covered Mars by MARSIS \aiOpenAccessSquare}, \ul{Geophysical Research Letters} 49(2), e2021GL096518, 7pp.
  
\item
  G. Steinbrugge, M. S. Haynes, D. M. Schroeder, K. M. Scanlan, A. Stark, D. A. Young, \textbf{C. Grima}, S. Kempf, G. Ng, D. Buhl, J. R.C. Voigt, T. Roatsch, and D. D. Blankenship$^\lozenge$, \texttt{(2022)}, \href{https://doi.org/10.1109/TGRS.2021.3134638}{Altimetry Measurements from Planetary Radar Sounders and Application to SHARAD on Mars}, \ul{IEEE Transactions on Geoscience and Remote Sensing}, vol. 60, 5109214,  pp. 1-14.
  
\item
  $\spadesuit$ K. M. Scanlan, D. A. Young, G. Steinbrügge, S. D. Kempf, \textbf{C. Grima}, and D. D. Blankenship$^\lozenge$, \texttt{(2021)}, \href{https://ieeexplore.ieee.org/document/9399772?source=authoralert}{Delay Doppler SAR Focusing and Quantitative Quality Control of Future REASON Data \aiOpenAccessSquare}, \ul{IEEE Journal of Selected Topics in Applied Earth Observations and Remote Sensing}, 14, pp. 4352-69.

\item
  $\spadesuit$ C. Gerekos, \textbf{C. Grima}, G. Steinbrugge, S. Thakur, K. M. Scanlan, D. A. Young, L. Bruzzone, D. D. Blankenship$^\lozenge$, \texttt{(2021)}, \href{https://doi.org/10.1016/j.icarus.2020.114197}{Martian roughness analogues of Europan terrains and implications on radar backscatter}, \ul{Icarus} 358, 114197, 17pp.
  
\item
  G. Steinbrugge, R.C. Voigt, D. Schroeder, A. Stark, M. Haynes, K. Scanlan, C. Hamilton, D. A. Young, H. Hussmann, \textbf{C. Grima}, D. D. Blankenship$^\lozenge$ , \texttt{(2020)}, \href{https://www.sciencedirect.com/science/article/abs/pii/S0019103519301526}{The Surface Roughness of Europa derived from Galileo Stereo Images}, \ul{Icarus} 343(113669), 15pp.
  
\item
  R. M. C. Lopes, S. D. Wall, C. Elachi, S. P. D. Birch, P. Corlies, A. Coustenis, A. G. Hayes, J. D. Hofgartner, M. A. Janssen, R. L. Kirk, A. LeGall, R. D. Lorenz, J. I. Lunine, M. J. Malaska, M. Mastroguiseppe, G. Mitri, C. D. Neish, C. Notarnicola, F. Paganelli, P. Paillou, V. Poggiali, J. Radebaugh, S. Rodriguez, A. Schoenfeld, J. M. Soderblom, A. Solomonidou, E. R. Stofan, B. W. Stiles, F. Tosi, E. P. Turtle, R. D. West, C. A. Wood, H. A. Zebker, J. W. Barnes, D. Casarano, P. Encrenaz, T. Farr, \textbf{C. Grima}, D. Hemingway, O. Karatekin, A. Lucas, K. L. Mitchell, G. Ori, R. Orosei, P. Ries, D. Riccio, L. A. Soderblom, and Z. Zhang,, \texttt{(2019)}, \href{https://ui.adsabs.harvard.edu/abs/2019SSRv..215...33L/abstract}{Titan as Revealed by the Cassini Radar}, \ul{Space Science Reviews} 215(4), 50 pp.
  
\item
  $\spadesuit$ L. M. Scanlan, \textbf{C. Grima}, G. Steinbrugge, S. D., Kempf, D. A. Young, D. D. Blankenship$^\lozenge$, \texttt{(2019)}, \href{https://www.sciencedirect.com/science/article/pii/S0032063319300820}{Geometric Determination of Ionospheric Total Electron Content from Dual Frequency Radar Sounding Measurements}, \ul{Planetary and Space Science} 178(104696), 11pp.

\item
  \textbf{C. Grima}, I. Koch, J. S. Greenbaum, K. M. Soderlund, D. D., Blankenship$^\lozenge$, D. A. Young, D. M. Schroeder, S. Fitzsimons, \texttt{(2019)}, \href{https://www.cambridge.org/core/journals/journal-of-glaciology/article/surface-and-basal-boundary-conditions-at-the-southern-mcmurdo-and-ross-ice-shelves-antarctica/3ED3BFD465A3F6A5FC48342694F91EC5}{Surface and Basal Boundary Conditions at the Southern McMurdo and Ross Ice Shelves, Antarctica \aiOpenAccessSquare}, \ul{Journal of Glaciology} 65(252), pp. 675-688.

\item
  A. Rutishauser, D.D. Blankenship$^\lozenge$, M. Sharp, M. L.Skidmore, J. S. Greenbaum, \textbf{C. Grima}, D. M. Schroeder, J. A. Dowdeswel and D. A. Young, \texttt{(2018)}, \href{http://advances.sciencemag.org/content/4/4/eaar4353}{Discovery of a hypersaline subglacial lake complex beneath Devon Ice Cap, Canadian Arctic \aiOpenAccessSquare}. \ul{Science Advances} 4(4), eaar4353, 6pp.
  
\item
  G. Steinbrugge, D.M. Schroeder, M.S. Haynes, H. Hussmann, \textbf{C. Grima}, D.D. Blankenship$^\lozenge$, \texttt{(2018)}, \href{https://www.sciencedirect.com/science/article/pii/S0012821X17306647}{Assessing the potential for measuring Europa's tidal Love number h2 using radar sounder and topographic imager data}, \ul{Earth and Planetary Science Letters}, Volume 482, pp. 334-341.
  
\item
  D. Castelletti, D. M. Schroeder, S. Hensley, \textbf{C. Grima}, G. Ng, D. Young, Y. Gim, L. Bruzzone, A. Moussessian and D. D. Blankenship$^\lozenge$, \texttt{(2017)}, \href{http://ieeexplore.ieee.org/abstract/document/8012547/}{\emph{An Interferometric Approach to Cross-Track Clutter Detection in Two Channel VHF Radar Sounders}}, \ul{IEEE Transactions on Geoscience and Remote Sensing} 55(11), pp.6128-40.

\item
  \textbf{C. Grima}, M. Mastrogiuseppe, A. G. Hayes, S. D. Wall, R. D. Lorenz, J. D. Gardner, B. Stiles, C. Elachi, \texttt{(2017)}, \href{http://www.sciencedirect.com/science/article/pii/S0012821X17303163}{Surface Roughness of Titan's Hydrocarbon Seas \aiOpenAccessSquare}, Earth and Planetary Science Letters 474, pp.20-24.
  
\item
  $\clubsuit$ A. Rutishauser, \textbf{C. Grima}, M. Sharp, D. D. Blankenship$^\lozenge$, D. Young, F. Cawkwell, J. Dowdeswell, \texttt{(2016)}, \href{http://onlinelibrary.wiley.com/doi/10.1002/2016GL071230/full}{Characterizing near-surface firn using the scattered signal component of the glacier surface return from airborne radio-echo sounding \aiOpenAccessSquare}, \ul{Geophysical Research Letters} 43(24), pp. 12502-10.
  
\item
  M. Golombek, D. Kipp, N. Warner, I. J. Daubar, R. Fergason, R. L. Kirk, R. Beyer, A. Huertas, S. Piqueux, N. E. Putzig, B. A. Campbell, G. A. Morgan, C. Charalambous, W. T. Pike, K. Gwinner, F. Calef, D. Kass, M. Mischna, J. Ashley, C. Bloom, N. Wigton, T. Hare, C. Schwartz, H. Gengl, L. Redmond, M. Trautman, J. Sweeney, \textbf{C. Grima}, I. B. Smith, E. Sklyanskiy, M. Lisano, J. Benardini, S. Smrekar, P. Lognonné, and W. B. Banerdt, , \texttt{2016}, \href{http://link.springer.com/article/10.1007/s11214-016-0321-9?wt_mc=Internal.Event.1.SEM.ArticleAuthorOnlineFirst}{Selection of the InSight Landing Site \aiOpenAccessSquare}, \ul{Space Science Reviews} 211(1–4), pp. 5–95.

\item
  N. E. Putzig, G. A. Morgan, B. A. Campbell, \textbf{C. Grima}, I. B. Smith, R. J. Phillips, M. P. Golombek, \texttt{(2016)}, \href{http://link.springer.com/article/10.1007\%2Fs11214-016-0322-8}{Radar derived Properties of the InSight Landing Site in Western Elysium Planitia on Mars \aiOpenAccessSquare}, Space Science Reviews 211(1–4), pp. 135–46.
  
\item
  D. M. Schroeder, B. Campbell, L. Bruzzone, A. Romero-Wolf, D. Blankenship$^\lozenge$, \textbf{C. Grima}, W. Kofman$^\lozenge$, L. Carrer, \texttt{(2016)}, \href{http://www.sciencedirect.com/science/article/pii/S0032063316301465}{Assessing the potential for passive radio sounding of Europa and Ganymede with RIME and REASON}, \ul{Planetary ans Space Science} 134,  pp. 52-60.
  
\item
  V. Poggiali, M. Mastrogiuseppe, A. Hayes, R. Seu, S. Birch, R. Lorenz, \textbf{C. Grima }, J. Kargel, J. Hofgartner, \texttt{(2016)}, \href{http://onlinelibrary.wiley.com/doi/10.1002/2016GL069679/abstract}{Liquid Filled Canyons on Titan \aiOpenAccessSquare}, \ul{Geophysical Research Letters} 43(15), pp. 7887-94.

\item
  \textbf{C. Grima}, J. S. Greenbaum, *E. Lopez Garcia, K. M. Soderlund, *\ul{A. Rosales}, D. D. Blankenship$^\lozenge$, D. A. Young, \texttt{(2016)}, \href{http://onlinelibrary.wiley.com/doi/10.1002/2016GL069524/pdf}{Radar detection of the brine extent at McMurdo Ice Shelf, Antarctica, and its control by snow accumulation \aiOpenAccessSquare}, \ul{Geophysical Research Letters} 43(13), pp. 7011-18.

\item
  T. Vance, J. Roberts, A. Moy, M. Curran, C. Tozer, A. Gallant, N. Abram, T. van ommen, D. Young, \textbf{C. Grima}, D. Blankenship$^\lozenge$, M. Siegert, \texttt{(2016)}, \href{http://www.clim-past.net/12/595/2016/cp-12-595-2016.pdf}{Optimal site selection for a high resolution ice core \aiOpenAccessSquare}. \ul{Clim. Past} 12, pp. 595-610.

\item
  \textbf{C. Grima}, D. D. Blankenship$^\lozenge$, D. M. Schroeder. \texttt{(2015)}, \href{http://www.sciencedirect.com/science/article/pii/S0032063315002470}{Radar Signal Propagation Through the Ionosphere of Europa}. \ul{Planetary and Space Science} 117, pp. 421-28.
  
\item
  D. M. Schroeder, \textbf{C. Grima}, D. D. Blankenship$^\lozenge$. \texttt{(2015)}, \href{http://library.seg.org/doi/abs/10.1190/geo2015-0122.1}{Evidence for Variable Grounding Zone Extent and Shear Margin Bed Conditions Across Thwaites Glacier, West Antarctica}. \ul{Geophysics} 81(1), 9pp.
  
\item
  B. Sánchez-Cano, D.D. Morgan, O. Witasse, S.M. Radicella, M. Herraiz, R. Orosei, M. Cartacci, A. Cicchetti, R. Noschese, W. Kofman$^\lozenge$, \textbf{C. Grima}, J. Mouginot, D.A. Gurnett, M. Lester, P.-L. Blelly, H. Opgenoorth and G. Quinsac, \texttt{(2015)}, \href{http://onlinelibrary.wiley.com/doi/10.1002/2014JA020630/abstract}{Total Electron Content in the martian atmosphere: a critical assessment of the Mars Express MARSIS datasets  \aiOpenAccessSquare}, \ul{Journal of Geophysical Research: Space Physics} 120(3), pp.2166-82.

\item
  \textbf{C. Grima}, D. D. Blankenship$^\lozenge$, D. A. Young, and D. M. Schroeder, \texttt{(2014)}, \href{http://onlinelibrary.wiley.com/enhanced/doi/10.1002/2014GL061635/}{Surface slope control on firn density at Thwaites Glacier, West Antarctica: Results from airborne radar sounding  \aiOpenAccessSquare}, \ul{Geophysical Research Letters} 41(19), pp.6787-94.

\item
  \textbf{C. Grima}, D. M. Schroeder, D. D. Blankenship$^\lozenge$, and D. A. Young, \texttt{(2014)}, \href{http://www.sciencedirect.com/science/article/pii/S0032063314002244}{\emph{Planetary landing zone reconnaissance using ice penetrating radar data: concept validation in Antarctica \aiOpenAccessSquare}}, \ul{Planetary and Space Science} 103, pp.191-204.

\item
  D. M. Schroeder, D. D. Blankenship$^\lozenge$, K. R. Raney, \textbf{C. Grima}, \texttt{(2014)},
  \href{http://ieeexplore.ieee.org/xpl/login.jsp?tp=\&arnumber=6901268\&url=http\%3A\%2F\%2Fieeexplore.ieee.org\%2Fstamp\%2Fstamp.jsp\%3Ftp\%3D\%26arnumber\%3D6901268}{Estimating subglacial water geometry using radar bed echo specularity: application to Thwaites Glacier, Antarctica \aiOpenAccessSquare}, \ul{IEEE Geoscience and Remote Sensing Letter} 12(3), pp.443-7.

\item
  \textbf{C. Grima}, \texttt{(2014)}, \emph{\href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?tp=\&arnumber=6827185\&queryText\%3Dgrima}{Comments on 'An inversion of Planetary Rough Surface Permittivity From Radar Sounder Observations'}}, IEEE Antenna and Wireless Propagation Letter, 13(1), pp.1-2.
  
\item
  J. Lasue, N. Mangold, E. Hauber, S. Clifford, W. Feldman, O. Gasnault, \textbf{C. Grima}, S. Maurice, O. Mousis, \texttt{(2013)},
  \href{https://link.springer.com/article/10.1007/s11214-012-9946-5}{Quantitative assessments of the martian hydrosphere \aiOpenAccessSquare}, \ul{Space Science Reviews}, 174(1-4), pp.155-212.
  
\item
  \textbf{C. Grima}, W. Kofman$^\lozenge$, A. Herique, R. Orosei, and R. Seu, \texttt{(2012)}, \href{http://www.sciencedirect.com/science/article/pii/S0019103512001558}{\emph{Quantitative analysis of Mars surface radar reflectivity at 20 MHz}}. \ul{Icarus}, 220, pp.84-99.
  
\item
  \textbf{C. Grima}, F. Costard, W. Kofman$^\lozenge$, B. Saint-Bézar, A. Servain, F. Rémy, J. Mouginot, A. Hérique, R. Seu, \texttt{(2011)}, \href{http://www.sciencedirect.com/science/article/pii/S0019103510004859}{Large asymmetric polar scarps on Planum Australe, Mars: Characterization and evolution \aiOpenAccessSquare}, \ul{Icarus}, 212(1), pp.96-109.

\item
  J. Mouginot, A. Pommerol, W. Kofman$^\lozenge$, P. Beck, B. Schmitt, A. Hérique, \textbf{C. Grima}, A. Safaeinili, J. J. Plaut, \texttt{(2010)},\href{https://www.sciencedirect.com/science/article/pii/S0019103510002757}{The 3-5MHz global reflectivity map of Mars by MARSIS/Mars Express: Implications for the current inventory of subsurface H2O  \aiOpenAccessSquare}, \ul{Icarus}, 210(2), pp.612-25.

\item
  A. Pommerol, W. Kofman$^\lozenge$, J. Audouard, \textbf{C. Grima}, P. Beck, J. Mouginot, A. Hérique,  A. Kumamoto, T. Kobayashi, T. Ono, \texttt{(2010)}, \href{http://onlinelibrary.wiley.com/doi/10.1029/2009GL041681/abstract}{Detectability of subsurface interfaces in lunar maria by the LRS/SELENE sounding radar: Influence of mineralogical composition  \aiOpenAccessSquare}. \ul{Geophysical Research Letters}, 37(3), pp.1-5.
  
\item
  \textbf{C. Grima}, W. Kofman$^\lozenge$, J. Mouginot, R. J. Phillips, A. Hérique, A., D. Biccari, R. Seu, M. Cutigni, \texttt{(2009)}, \href{http://onlinelibrary.wiley.com/doi/10.1029/2008GL036326/abstract}{North polar deposits of Mars: Extreme purity of the water ice \aiOpenAccessSquare}. \ul{Geophysical Research Letters}, 36(3), pp.2-5.
  
\item
  J. Mouginot, W. Kofman$^\lozenge$, A. Safaeinili, \textbf{C. Grima}, A. Hérique, J. J. Plaut, \texttt{(2009)}, \href{http://www.sciencedirect.com/science/article/pii/S0019103509000311}{MARSIS surface reflectivity of the south residual cap of Mars \aiOpenAccessSquare}, \ul{Icarus}, 201(2), pp.454-459.
  
\item
  H. Gunell$^\lozenge$, U. V. Amerstorfer, H. Nilsson, \textbf{C. Grima}, M. Koepke, M. Fränz, J. D. Winningham, R. A. Frahm, J.-A. Sauvaud, A. Fedorov, \texttt{(2008)} \href{http://iopscience.iop.org/0741-3335/50/7/074018}{Shear driven waves in the induced magnetosphere of Mars \aiOpenAccessSquare}. \ul{Plasma Physics and Controlled Fusion}, 50(7), 074018, 9pp.

\end{etaremune}
