\section*{Academic and Technical Reports}

\begin{etaremune}
\def\labelenumi{\arabic{enumi}.}

\item
   \textbf{Grima C.}, Y. Okumura, D. Blankenship, L. Lavier, \texttt{(2024)}, \emph{Committee for Disability \& Access (D\&A) Equipment and Accommodation.}, UTIG Retreat White Paper.
   
\item 
   I-MIM MDT (inc. \textbf{Grima C.}) (2022) \href{https://smd-cms.nasa.gov/wp-content/uploads/2023/10/i-mim-mdt-final-report-31-aug-2022-final-hi-qual-copy-tagged.pdf}{Final Report of the International Mars Ice Mapper Reconnaissance/Science Measurement Definition Team}. 239 pp., ASI/CSA/JAXA/NASA/NSO.
   
\item
   Gerekos C, \textbf{Grima C.}. \texttt{(2022)}, \emph{On IEM and Fractal Backscattering Laws for REASON Measurement Quality Verification and Validation}, Jet Propulsion Laboratory Interoffice Memorandum, IOM-REASON-2022-003.
   
\item
   Young D. A., N. Wolfenbarger, T. Richter, \textbf{C. Grima} and K. Soderlund, \texttt{(2019)}, \emph{Science Verification and Validation Point Models for REASON}, Jet Propulsion Laboratory Interoffice Memorandum, IOM-REASON-2019-001.
   
\item
  \textbf{Grima C.}, \texttt{(2017)}, \emph{Europa Radio Noise Shadow},
  Jet Propulsion Laboratory Interoffice Memorandum, IOM-REASON-2017-001.
  
\item
  \textbf{Grima C.}, \texttt{(2014)}, \emph{Europa Space Environment and
  Radar Operations}, White paper for the "Ice Penetrating Radar team for
  the Instrument Concept for Europa Exploration" (ICEE) program
  (JPL/NASA).
  
\item
  Schroeder D.M., \textbf{Grima C.}, Blankenship D.D., \texttt{(2012)},
  \emph{Assessing the Utility of the Europe Clipper Radar Sounder to
  Identify Potential Landing Sites}, White paper for the "Europa Science
  Definition Team", July 2012.
  
\item
  \textbf{Grima C.}, \texttt{(2011)},
  \href{https://www.google.com/url?sa=t\&rct=j\&q=\&esrc=s\&source=web\&cd=2\&ved=0ahUKEwiu-Jn8t7LPAhWEOSYKHQOlBeUQFggrMAE\&url=http\%3A\%2F\%2Fwww.theses.fr\%2F2011GRENU004.pdf\&usg=AFQjCNFcVxpOJiku0pWYrUsHbDrZU01hiA\&sig2=RAzQ2GJJIpOr1U3PEjRsXw}{Surface
  et subsurface de Mars par sondage radar : Analyse des données
  MRO/Sharad}, Thèse de doctorat, Université de Grenoble.
  
\item
  \textbf{Grima C.}, Witasse O., and Orosei R., \texttt{(2009)},
  \href{https://archives.esac.esa.int/psa/ftp/MARS-EXPRESS/MARSIS/MEX-M-MARSIS-5-DDR-SS-TEC-V1.0/DOCUMENT/MARSIS_EAICD_TEC.PDF}{MEX-MARSIS subsurface (SS) mode: Total electron content (TEC) of the ionosphere level 5 derived data. Experimenter to planetary archive interface control document (EAICD)}. European Space Agency.
  
\item
  \textbf{Grima, C.}, and Kofman, W., \texttt{(2008)}, \href{https://archives.esac.esa.int/psa/ftp/MARS-EXPRESS/MARSIS/MEX-M-MARSIS-5-DDR-SS-TEC-V1.0/DOCUMENT/IONOPROCESS_REPORT1.PDF}{Ionospheric impact on MARSIS radar signal}. ESA European Space Agency contract report No 21646/08/NL/NR, volume 1.
  
\item
  \textbf{Grima, C.}, and Kofman, W., \texttt{(2008)}, \href{https://archives.esac.esa.int/psa/ftp/MARS-EXPRESS/MARSIS/MEX-M-MARSIS-5-DDR-SS-TEC-V1.0/DOCUMENT/IONOPROCESS_REPORT2.PDF}{Correcting
  the ionospheric impact on MARSIS radar signal}. European Space Agency
  study contract report No 21646/08/NL/NR, volume 2.
  
\item
  \textbf{Grima, C.}, and Kofman, W., \texttt{(2008)}, \href{https://archives.esac.esa.int/psa/ftp/MARS-EXPRESS/MARSIS/MEX-M-MARSIS-5-DDR-SS-TEC-V1.0/DOCUMENT/IONOPROCESS_REPORT3.PDF}{MARSIS
  derived enhanced ionospheric calibration data}. European Space Agency
  study contract report No 21646/08/NL/NR, volume 3.
\end{etaremune}
